A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-14 manuscript/manuscript.tex
manuscript format

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}

@@

\author
{Carter Allen\emailx{allecart@musc.edu} \\
Department of Public Health Sciences, Medical University of South Carolina, Charleston, SC, U.S.A
\and
Brian Neelon, PhD\emailx{neelon@musc.edu} \\
Department of Public Health Sciences, Medical University of South Carolina, Charleston, SC, U.S.A
\and
Sara Benjamin-Neelon, PhD, MPH, RD\emailx{sara.neelon@jhu.edu} \\
Department of Health, Behavior and Society, Johns Hopkins University, Baltimore, MD, U.S.S}

@@

>>>>

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{blindtext}

@@

\author
{Carter Allen\emailx{allecart@musc.edu} \\
Department of Public Health Sciences, Medical University of South Carolina, Charleston, SC, U.S.A
\and
Brian Neelon, PhD \\
Department of Public Health Sciences, Medical University of South Carolina, Charleston, SC, U.S.A
\and
Sara Benjamin-Neelon, PhD, MPH, RD \\
Department of Health, Behavior and Society, Johns Hopkins University, Baltimore, MD, U.S.S}

@@

A primary concern of our model is with identification of latent infant development clusters. We accomplish this via multinomial logit regression model on cluster membership, which utilizes P\'{o}lya-Gamma data-aumentation to allow for updating of all parameters using Gibbs sampling. The multinomial logit model is as follows for $l = 1,...,h$.

$$P(Z_i = l|w_i) = \pi_{il} = \frac{e^{w_i^T \delta_l}}{\sum_{r = 1}^h e^{w_i^T \delta_r}}$$

where $w_i$ is the vector of class probability covariates for subject $i$, $\delta_l$ contains the multinomial regression parameters for class $l$, and $h$ is the number of putative clusters specified \textit{a priori}.

During our MCMC estimation procedure, the class labels $z_i$ are updated from their multinomial full conditional distribution and used in the remaining MCMC steps as class assignments.
